---
title: "lab_report_knapsack"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lab_report_knapsack}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, eval=FALSE}
library(KnapSacked)
```

# Introduction

## 1.1.2 Brute force search

```{r, eval=F}
# Function to get time
get_time <- function(i){
  time <- system.time(expr = brute_force_knapsack(x = knapsack_objects[1:16,], W=i))[3]
  return(time)}

# Function to get mean execution time
mean(unlist(lapply(c(10,100,1000,10000, 100000), FUN = get_time)))
```

- **Question:** How much time does it takes to run the algorithm for n = 16 objects?
  - Average Code Execution Time: **2.004 seconds**
  
## 1.1.3 Dynamic Programming

```{r, eval=F}
# Data Object
n <-1000000
knapsack_objects <-
  data.frame(
    w=sample(1:4000, size = n, replace = TRUE),
    v=runif(n = n, 0, 10000)
  )
# Function to get time
get_time <- function(i){
  time <- system.time(expr = knapsack_dynamic(x = knapsack_objects[1:500,], W=i))[3]
  return(time)}

# Function to get mean execution time
mean(unlist(lapply(c(100,500,1000,1500,2000,3000,4000,5000), FUN = get_time)))
```

- **Question:** How much time does it takes to run the algorithm for n = 500 objects?
  - Average Code Execution Time: **2.65 seconds**

## 1.1.4 Greedy Heuristics

```{r, eval=F}
# Data Object
n <-1000000
knapsack_objects <-
  data.frame(
    w=sample(1:4000, size = n, replace = TRUE),
    v=runif(n = n, 0, 10000)
  )
# Function to get time
get_time <- function(i){
  time <- system.time(expr = greedy_knapsack(x = knapsack_objects[1:1000000,], W=i))[3]
  return(time)}


mean(unlist(lapply(c(1000,2500,5000,10000,15000,20000), FUN = get_time)))

# Function to get mean execution time
mean(unlist(lapply(c(1000,2500,5000,10000,15000,20000), FUN = get_time)))
```

- **Question:** How much time does it takes to run the algorithm for n = 1000000 objects?
  - Average Code Execution Time: **0.34 seconds**
  
## 1.1.6 Profile your code and optimize your code

- **Question:** What performance gain could you get by trying to improving your code?
  - Implemented:
    - **_Code Organization_** : Reduced no. of operations per function, saving time on multiple code block execution.
    - **_Vectorization_** : Replaced loops with Vectorization wherever possible, which reduced code execution time
    - **_Parallelization_** : Added Parallel programming for Windows machine, which boosted execution time for large no. of values in 'brute_force_knapsack' program.
    
## 1.1.7 Parallelize brute force search

- Set parameter `parallel = T` 

```{r, eval=F}
brute_force_knapsack(x = knapsack_objects[1:8,], W = 3500, parallel = T)
brute_force_knapsack(x = knapsack_objects[1:8,], W = 2000, parallel = T)
```

# 1.2 Profile and improve your existing API package

## Solution-1: Add Memoization to reduce API calls overhead

```{r, eval=F}
install.packages("memoise")

library(memoise)

f <- memoise(func)
```
## Solution-2: Chunking

- Limited no. of trials per call to 10,000 only.
